Type-theoretical Semantics of \Pio\ via the Delay Monad \thanks{Supported by organization x.}

### 2019-04-24 mpc19/paper.tex

It is well-known that a trace operator is obtainable from an iteration
operator. This is how Hasegawa's construction  \cite{Hasegwa97} derives it in the following way:
\begin{align*}
& \traceD : (A + B \to \Delay (A + C)) \to B \to \Delay C \\
& \traceD \,f = \copairD{\iterD \,\mapL f}{\now} \diamond \mapR f
\end{align*}

@@

%\ctikzfig{language}

>>>>

\ctikzfig{fL_fR}
\ctikzfig{trace}

It is well-known that a trace operator is obtainable from an iteration
operator, as shown by Hasegawa  \cite{Hasegawa97}. His construction,
instantiated to our setting, looks like this:
\begin{align*}
& \traceHD : (A + B \to \Delay (A + C)) \to B \to \Delay C \\
& \traceHD \,f = \iterD (\Delay (\inl + \id) \comp f) \comp \inr
\end{align*}

@@
